\begin{frame}
\frametitle{Irrationality of smooth cubic threefolds}

The theory of Pryms can be used to prove irrationality of some special varieties. Here we sketch the ideas involved.
\pause

\begin{itemize}
	\item ``Schottky problem'' for Pryms. Which abelian varieties are Prym varieties? (more general than Jacobians).
	\begin{theorem}[Shokurov]
	Let $g \neq 4$. If $\Prym(\widetilde C, C)$ is a Jacobian, then $C$ is hyperelliptic, trigonal, or a plane quintic with $h^0(\OO_C(1) \otimes \eta)=0$. 
	\end{theorem}
	\pause
	\item We want to violate this condition.
\end{itemize}

\begin{theorem}[Clemens--Griffiths criterion]
If $X$ is rational, then $J(X)$ is a Jacobian or a product of Jacobians.
\end{theorem}

\end{frame}

\begin{frame}
\frametitle{Intermediate Jacobians}

\begin{itemize}
	\item Want to mimic the definition of ordinary Jacobians for more general varieties.
	\pause
	\item Often no natural polarization to choose.
	\pause
	\item For simplicity: if $X$ is a smooth threefold with $h^{3,0}=0$, then we define its \alert{intermediate Jacobian} as
	\[
	J(X) \defeq H^{1,2}(X)/H^3(X,\Z).
	\]
	The intersection form on $H^3(X,\Z)$ defines in this case a principal polarization.
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Proof of irrationality of cubic threefold}

\begin{enumerate}
	\item Choose $\ell \subset X$ and blow up $X_\ell \to X$.
	\pause
	\item The projection from $\ell$ to a generic $\P^2$ defines a morphism $X_\ell \to \P^2$ inducing the structure of a conic bundle on $X_\ell$.
	\pause
	\item Can show that the blow-up doesn't change the intermediate Jacobian $J(X)=J(X_\ell)$.
	\pause
	\item The discriminant curve $C$ of $X_\ell \to \P^2$ is a smooth quintic. The fibers are pairs of lines (=degenerate conics). This gives $\widetilde C \xrightarrow{2:1} C$.
	\pause
	\item But $h^0(\OO_C(1) \otimes \eta)=1 \implies J(X)$ is not a Jacobian.
	\pause
	\item So $X$ cannot be rational!
\end{enumerate}

\end{frame}
