\begin{frame}
\frametitle{Maps between moduli spaces}

\begin{itemize}
	\item Let $\A_g$ denote the moduli space of principally polarized abelian varieties \big(dimension $d(d+1)/2$\big).
	\pause

	\item Let $\mathfrak M_g$ denote the moduli space of genus $g$ curves.
	\pause
	\item Let $R_g$ denote the space of double covers $\widetilde C \to C$. It can identified with
	\[
	R_g = \{ [C,\eta] \mid C \in \mathfrak M_g, \eta \in \Pic^0(C) \backslash \{ \OO_C\}, \eta^{\otimes 2}=\OO_C \}.
	\]

\end{itemize}
\unskip\vskip1ex
\only<4->{
\[
\xymatrix{
 & R_g \ar[dl]_{\pi_1} \ar[dr]^{\Pr}  & \\
\mathfrak M_g & & \A_{g-1}
}
\]

The forgetful map is a $\left(2^{2g}-1\right)$-cover. 
}

\end{frame}


\begin{frame}
\frametitle{The Prym map}

The structure of the map $\Pr\colon R_g \to \A_{g-1}$ is very interesting (analogue of the Torelli map $J\colon\mathfrak M_g \to \A_g$).

\pause

\begin{theorem}[Generic Torelli]

For $g \geq 7$, the Prym map is generically injective. 

\end{theorem}
\pause

It is however \alert{never} injective, because of Donagi's \alert{tetragonal construction}, which we are now going to explain.
\end{frame}

\begin{frame}
\frametitle{The tetragonal construction (Donagi)}

\begin{itemize}
	\item Recall that a curve is \alert{tetragonal} if it admits a $4:1$ map $C \xrightarrow{f} \P^1\mkern-4mu$.
	\pause
	\item Let $\widetilde C \xrightarrow{\pi} C$ be a double covering.
	\pause
	\item Consider the symmetric product ${\widetilde C}^{(4)} \subset \Pic^4(\widetilde C)$.
\end{itemize}
\pause

Consider the Cartesian diagram:

\[
\xymatrix{
f_\ast \widetilde C = \left\{ (D,p) \mid f^{(4)}(\Nm(D)) = \widetilde f (p) \right\} \ar[r] \ar[dd]_{\widetilde f} & {\widetilde C}^{(4)} \ar[d]^{\pi^{(4)}} \\
 & C^{(4)} \ar[d]^{f^{(4)}} \\
\P^1 \ar[r]^\Delta & {(\P^1)}^{(4)} = \P^4
}
\]
\end{frame}

\begin{frame}
\frametitle{The tetragonal construction (continued)}

\begin{enumerate}[<+->]
	\item The involution of $\widetilde C$ acts on $f_\ast \widetilde C$ as well.

	\item There is an equivalence relation in $f_\ast \widetilde C$ defined as follows:
	\[
	(D,p) \sim \big(D',p'\big) \iff
	\begin{cases}
	\#(D \cap D') \equiv 0 \pmod 2 \\
	p = p'
	\end{cases}
	\]

	\item Then I (Donagi, really) claim the following:
	\begin{enumerate}
		\item $\widetilde f\colon f_\ast \widetilde C = C_1 \sqcup C_2 \to \P^1\mkern-4mu$, with $C_i$ tetragonal.
		\item $C_i \to C_i/\iota$ are unramified double coverings.
		\item Their associated Pryms are equal!
		\[
		\Prym(\widetilde C, C)=\Prym(C_1,C_1/\iota)=\Prym(C_2,C_2/\iota).
		\]
	\end{enumerate}
\end{enumerate}



\end{frame}
